% !Mode:: "TeX:UTF-8"

\begin{Eabstract}{Searchable Encryption}{Access Control}{Privacy Preserving}{Attribute Based Encryption}{Cloud Computing Security}
 e Cloud Computing is regarding as a promising technology to facilitate the data sharing such that many organizations and individual users share data with each other by outsourcing their sensitive and critical data to the remote Cloud Storage Provider (CSP). With the advent of cloud computing, the computational and storage resources can be obtained by the user in a pay-per-use manner from anywhere and anytime. Despite of numerous advantages of cloud computing, it is not an easy task to ensure the security of sharing data since the CSP is usually considered to be untrusted. One natural method to protect the confidentiality of sharing data stored in the CSP is to utilize the public-key encryption technique because the function of public-key cryptography is more flexible than the symmetric encryption. However, the simple deployment of traditional public-key encryption mechanism in cloud computing environment faces some challenges. First of all, the traditional public-key encryption can only offer one-to-one encryption and thus only coarse-grained access control. Second, the search function cannot be performed over the encrypted data directly.\par
To address these issues, in this thesis, we concentrates on the one-to-many authentication and underlying techniques such as the attribute-based encryption, broadcast encryption and fuzzy public key encryption. Moreover, we also focus on the public key encryption with keyword search. It is noted that we only concentrate on the techniques to ensure the confidentiality of sharing data in the cloud computing. That is to say, the authentication, unforgeability and non-repudiation of the sharing data is outside the scope of our thesis. Precisely speaking, the main contribution of our thesis consist of the following parts:
\begin{enumerate}
	\item We present in this research Conjunctive Keywords Searchable over Attribute-Based Encryption CKSABE as novel scheme, which can allow an authorized user to ask Cloud server for fetching conventional keywords conjunctively, which has been encrypted under Attribute Base Policy ABE. And Cloud can search over the encrypted data without disclosing any information related to the secret keywords in efficient time and high precision. The proposed scheme in this thesis considers devices which are low and limited resources, which has few amount of processing power, to meet the short of this machines we deduced the computation cost on the client side by removing all bilinear pairing from the customer to the Cloud side.
	\item Broadcast Searchable Keywords Encryption (BSKE) is a novel method, which broadcast encrypted keywords for all users in a set (group), and enable any users of the set to search for particular keyword by asking a Cloud provider if the encrypted keyword exists or not without breaking the privacy of broadcaster and questioner assuming that the cloud provider is untested party. BSKE scheme has constant and short size O(3), efficient revocable for users without reset security parameters and the computation's complexity in the Cloud side only. BSKE designed based on random oracle model and the scheme is secure against adaptive chosen keyword attack.
	\item In this thesis, we proposed a novel applicable Public Key Fuzzy Searchable encryption (PKFSE), which is secure under random model assuming DDH assumption is held. The fuzzy searching function is efficient with short public key O(1), private key O(1), Index O(Wn) and Trapdoor O(Wn), where Wn is number of character in the keyword W. Also, we demonstrate the general primitive operations of fuzzy searching such as insertion, deletion and substitution. The proposed scheme has less computation cost in the client sides for both Data Owners and Data Users which can deploy in low resources machines.
	\item We propose a new practical Revocable Attribute Based Encryption which has a short ciphertext O(1) and private keys O(1) with efficient running time. In this scheme the users can effectively be revoked and added with backward and forward secrecy in the indirect mode, which can controlled by Key Authority Party without reseting the system parameter's or updating and redistributing the attributes private keys which has expense. Assuming the Cloud provider is semi-honest and has been delegated by KA in order to apply dynamic processing on the data and controlling users. We introduce scheme secured against Chosen Plaintext Adversary(CPA), assuming the (Decision) Bilinear Diffie-Hellman Exponent assumption (n-BDHE) is being held.
\end{enumerate}
\end{Eabstract}
